ms_figures

### 2022-11-14 ms_figures.Rmd
update ms figures and results summary

library(tidyverse)
library(countrycode)
library(circlize)
library(here)
library(ggpubr)
library(kableExtra)
library(DBI)
library(janitor)
library(viridis)
library(broom)
library(exploreARTIS)
library(vegan)

@@

@@

```{r set_directories}
# Set time series dates
date_nodash <- "20220614"
date_dash <- "2022-06-14"

# Set directories 
# datadir <-  paste("/Volumes/jgephart/ARTIS/Outputs/S_net/", date_nodash, "_ARTIS-timeseries", sep="")
model_inputs_dir <- "/Volumes/jgephart/ARTIS/Outputs/model_inputs_archive_20220718"
outdir <- "/Volumes/jgephart/ARTIS/Outputs/ms_seafood_globalization"

# Set color palettes
# All colors from palette: #FFE6BE (light yellow), #F7AF75 (light orange), #F37542 (medium orange), 
# #E24027 (dark orange), #0F2D59 (navy), #1B708F (blue), #2E8D9A (teal), #86ADA7 (light blue)
method_colors <- c("#F7AF75", "#2E8D9A", "#86ADA7") # light orange, teal, light blue
source_colors <- c("#F37542", "#0F2D59", "#86ADA7") # medium orange, navy, light blue

@@

@@

```{r join_data}
# Load cleaned FAO production data
prod <- prod %>% 
  select("year", "iso3c", "sciname", 
         "method" = "prod_method", "environment", 
         "production_t" = "live_weight_t") %>%
  group_by(year, iso3c, sciname, method, environment) %>%
  summarise(production_t = sum(production_t, na.rm = TRUE)) %>%
  ungroup()

# Join production data to ARTIS
artis <- artis %>%
  filter(live_weight_t >= 0.1) %>%
# FIX IT: Determine if this should be deleted. Production of only species exports may not be relevant
  left_join(prod, by = c("year", "exporter_iso3c" = "iso3c", 
                           "sciname", "method", "environment")) %>%
  ungroup()

# Update artis data to lowest resolution by comparing code taxa_level and prod taxa_level
artis <- artis %>%
  # FIX IT: Change metadata to HSXX format and then remove this line
  mutate(hs_version = as.integer(parse_number(hs_version))) %>%
  left_join(code_max_resolved_taxa,
            by = c("hs_version", "hs6", "sciname")) %>%
  left_join(sciname_metadata, 
            by = c("sciname" = "SciName")) %>%
  # Leave any missing sciname_hs_modified as original sciname
  mutate(sciname_hs_modified = case_when(
    is.na(sciname_hs_modified) ~ sciname,
    TRUE ~ sciname_hs_modified
  ))

@@

@@

@@

@@

```{r SI_top_traders}
total_country_exports <- artis %>% 
  group_by(exporter_iso3c, method, environment) %>%
  summarise(export_live_weight_t = sum(live_weight_t)/length(2015:2019)) %>%
  mutate(export_live_weight_t = export_live_weight_t/1000000) %>%
  rename("iso3c" = "exporter_iso3c")

total_country_imports <- artis %>% 
  group_by(importer_iso3c, method, environment) %>%
  summarise(import_live_weight_t = sum(live_weight_t)/length(2015:2019)) %>%
  mutate(import_live_weight_t = import_live_weight_t/1000000) %>%
  rename("iso3c" = "importer_iso3c")

```{r top_imp_exp}
# Top exporters, averaged over beginning and end time periods
top_exp_1 <- artis %>% 
  filter(year %in% 1996:2000) %>%
  group_by(exporter_iso3c, method) %>%
  summarise(live_weight_t = sum(live_weight_t)/length(1996:2000)) %>% 
  ungroup() %>%
  group_by(exporter_iso3c) %>%
  mutate(total = sum(live_weight_t)) %>%
  ungroup() %>%
  mutate(exporter_iso3c = fct_reorder(as.factor(exporter_iso3c), total)) %>%
  slice_max(n = 60, order_by = total) %>%
  ggplot(aes(x = live_weight_t/1000000, y = exporter_iso3c, fill = method)) +
  geom_bar(stat="identity", position = "stack") + 
  scale_fill_manual(values = method_colors) +
  lims(x = c(0, 10)) +
  labs(x = "Seafood exports (million t, live weight)", y = "",
       title = "Top 20 seafood \nexporters (1996-2000)", fill = "Production method") +
  theme_minimal()

@@

@@

```{r regional_bilateral_trends}
artis_region <- artis %>%
  mutate(importer_region = countrycode(importer_iso3c, origin = "iso3c", destination = "continent"),
         exporter_region = countrycode(exporter_iso3c, origin = "iso3c", destination = "continent")) %>%
  filter(!is.na(importer_region), !is.na(exporter_region)) %>%
  group_by(year, exporter_region, importer_region) %>%
  summarise(live_weight_t = sum(live_weight_t)) %>%
  ungroup() %>%
  mutate(exporter_importer = paste(exporter_region, " to ", importer_region, sep = ""))

@@

```{r region_trend_matrix, fig.height=6, fig.width=6}
artis_region %>%
  ggplot(aes(x = year, y = live_weight_t/1000000, color = slope/1000)) +
  geom_line(size = 2) +
  scale_color_gradient2(low = "#E24027", mid = "grey70", high = "#1B708F") +
  labs(x = "", y = "Exports (million t)", color = "Ave. annual change in export \n(1000 t live weight)") +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1), 
        legend.position = "bottom") +
  facet_grid(rows = vars(exporter_region), cols = vars(importer_region), 
             labeller = label_wrap_gen(width = 5))

@@

# Figure 3:

```{r calculate_supply}
exports <- artis %>%
  group_by(year, exporter_iso3c, dom_source, sciname, CommonName, method, environment) %>%
  summarise(live_weight_t = sum(live_weight_t)) %>%
  mutate(dom_source = str_replace(dom_source, " ", "_")) %>%
  pivot_wider(names_from = "dom_source", values_from = "live_weight_t")

imports <- artis %>%
  group_by(year, importer_iso3c, sciname, CommonName, method, environment) %>%
  summarise(imports_live_weight_t = sum(live_weight_t))

supply <- exports %>%
  full_join(imports, by = c("year", "exporter_iso3c" = "importer_iso3c", 
                            "sciname", "CommonName", "method", "environment")) %>%
  full_join(prod, by = c("year", "exporter_iso3c" = "iso3c", 
                          "sciname", "method", "environment"))

supply$foreign_export[is.na(supply$foreign_export)] <- 0
supply$domestic_export[is.na(supply$domestic_export)] <- 0
supply$error_export[is.na(supply$error_export)] <- 0
supply$imports_live_weight_t[is.na(supply$imports_live_weight_t)] <- 0
supply$production_t[is.na(supply$production_t)] <- 0

supply <- supply %>%
  mutate(supply = production_t + imports_live_weight_t - domestic_export - foreign_export - error_export,
         supply_no_error = production_t + imports_live_weight_t - domestic_export - foreign_export, 
         supply_domestic = production_t - domestic_export,
         supply_foreign = imports_live_weight_t - foreign_export) %>%
  rename("iso3c" = "exporter_iso3c") %>%
  ungroup() %>%
  mutate(supply_no_error = replace_na(supply_no_error, 0),
         supply_domestic = replace_na(supply_domestic, 0),
         supply_foreign = replace_na(supply_foreign, 0))

@@

Foreign dependence trends
Where does trade have a positive versus negative effect on per capita supply for capture versus aquaculture? 
Does trade increase the diversity of supply and if so, where?

## Effect of trade on supply diversity

```{r supply_diversity}
# FIX IT: The new prod data is in here, so it doesn't merge correctly with the trade data (potentially leading to many negative supply values)

# FIX IT: Make sure supply calc includes supply of non-traded species

>>>>

library(tidyverse)
library(countrycode)
library(circlize)
library(here)
library(ggpubr)
library(kableExtra)
library(DBI)
library(janitor)
library(viridis)
library(broom)
library(exploreARTIS)
library(vegan)
```

@@

country_metadata <- dbGetQuery(con, "SELECT * FROM countries")
country_metadata <- country_metadata %>%
  select(-record_id)

@@

```{r set_directories}
# Set time series dates
date_nodash <- "20220926"
date_dash <- "2022-09-26"

# Set directories 
model_inputs_dir <- "/Volumes/jgephart/ARTIS/Outputs/model_inputs_20220926"
outdir <- "/Volumes/jgephart/ARTIS/Outputs/ms_seafood_globalization"

# Set color palettes
# All colors from palette: #FFE6BE (light yellow), #F7AF75 (light orange), #F37542 (medium orange), 
# #E24027 (dark orange), #0F2D59 (navy), #1B708F (blue), #2E8D9A (teal), #86ADA7 (light blue)
method_colors <- c("#F7AF75", "#2E8D9A", "#86ADA7") # light orange, teal, light blue
source_colors <- c("#F37542", "#0F2D59", "#86ADA7") # medium orange, navy, light blue
environment_colors <- c( "#2E8D9A", "#0F2D59","#86ADA7") # teal, navy, light blue

habitat_source_colors <- c("#1B708F", # blue = marine capture
                          "#86ADA7", # light blue = freshwater capture
                          "#F37542", # medium orange = marine aquaculture
                          "#F7AF75", # light orange = inland aquaculture
                          "grey50" # unknown
                          )

region_colors <- c(
  "#741A32", # maroon
  "#B34232", # burnt orange
  "#D38F35", #  orange
  "#D4B95f", # khaki
  "#4FA2A2", # teal
  "#114F59" # dark teal
)

@@

pop <- read.csv("/Volumes/jgephart/ARTIS/Outputs/clean_metadata/fao_annual_pop.csv") %>% 
  left_join(country_metadata, by = c("iso3c")) %>%
  select(iso3c, year, "region" = "owid_region", pop)

@@

```{r join_data}
# Load cleaned FAO production data
prod <- prod %>% 
  select("year", "iso3c", "sciname", 
         "method", "habitat", 
         "production_t" = "live_weight_t") %>%
  group_by(year, iso3c, sciname, method, habitat) %>%
  summarise(production_t = sum(production_t, na.rm = TRUE)) %>%
  ungroup()

# Join production data to ARTIS
artis <- artis %>%
  filter(live_weight_t >= 0.1) %>%
  # Add importer and exporter region
  left_join(country_metadata %>% 
              select("exporter_iso3c" = "iso3c", "exporter_region" = "owid_region"), by = c("exporter_iso3c")) %>%
  left_join(country_metadata %>% 
              select("importer_iso3c" = "iso3c", "importer_region" = "owid_region"), by = c("importer_iso3c")) %>%
# FIX IT: Determine if this should be deleted. Production of only species exports may not be relevant
  left_join(prod, by = c("year", "exporter_iso3c" = "iso3c", 
                           "sciname", "method", "habitat")) %>%
  ungroup()

# Update artis data to lowest resolution by comparing code taxa_level and prod taxa_level
artis <- artis %>%
  # FIX IT: Change metadata to HSXX format and then remove this line
  mutate(hs_version = as.integer(parse_number(hs_version))) %>%
  left_join(code_max_resolved_taxa,
            by = c("hs_version", "hs6", "sciname")) %>%
  left_join(sciname_metadata, 
            by = "sciname") %>%
  # Leave any missing sciname_hs_modified as original sciname
  mutate(sciname_hs_modified = case_when(
    is.na(sciname_hs_modified) ~ sciname,
    TRUE ~ sciname_hs_modified
  )) %>%
  rename(environment = habitat) %>%
  # Add habitat-method column
  mutate(habitat_method = paste(environment, method, sep =" ")) %>% 
  mutate(habitat_method = case_when(
    str_detect(habitat_method, "unknown") ~ "unknown", 
    TRUE ~ habitat_method
  )) %>% 
  # Set factor levels
  mutate(habitat_method = factor(habitat_method, levels = c("marine capture", "inland capture",
                                                            "marine aquaculture", "inland aquaculture",
                                                            "unknown" )))

@@

```{r fig1a}
global_export_by_source <- artis %>% 
  mutate(food_or_fmfo = case_when(
    hs6 == "230120" ~ "fishmeal",
    hs6 != "230120" ~ "nonfishmeal"
  )) %>%
  group_by(year, habitat_method, food_or_fmfo) %>%
  summarise(live_weight_t = sum(live_weight_t))

write.csv(global_export_by_source, "outputs/global_export_by_source.csv", row.names = FALSE)

global_export_by_source <- global_export_by_source %>%
  group_by(year, habitat_method) %>%
  summarise(live_weight_t = sum(live_weight_t)) %>%
  ggplot(aes(x = year, y = live_weight_t/1000000, fill = habitat_method)) +
  geom_area() +
  scale_fill_manual(values = habitat_source_colors) +
  labs(y = "Exports (mil. t, live weight)", fill = "Source", x = "") +
  theme_bw() +
  theme(legend.position = "bottom")

@@

```{r fig1b}
prod_by_source <- prod %>%
  group_by(year, method, habitat) %>% 
  summarise(production_t = sum(production_t)) %>%
  mutate(habitat_method = paste(habitat, method, sep = " ")) %>%
    # Set factor levels
  mutate(habitat_method = factor(habitat_method, 
                                 levels = c("marine capture", "inland capture",
                                            "marine aquaculture", "inland aquaculture"))) %>%
  ungroup() %>%
  select(-habitat, -method)

dom_export_by_source <- artis %>% 
  filter(dom_source == "domestic export") %>%
  group_by(year, habitat_method, environment) %>%
  summarise(dom_live_weight_t = sum(live_weight_t))

# One attempt to include unknown - would probably need to revisit this (perhaps by country, though that would ignore the possibility of it being sourced from elsewhere)

# unknown_habitat_export<- artis %>% 
#   filter(dom_source == "error export", environment == "unknown") %>%
#   group_by(year) %>%
#   summarise(unknown_habitat_live_weight_t = sum(live_weight_t)) 
# 
# unknown_method_export<- artis %>% 
#   filter(dom_source == "error export", environment != "unknown") %>%
#   group_by(year, environment) %>%
#   summarise(unknown_method_live_weight_t = sum(live_weight_t))

# dom_export_by_source %>%
#   left_join(unknown_habitat_export, by = c("year")) %>%
#   left_join(unknown_method_export, by = c("year", "environment")) %>%
#   left_join(prod_by_source, by = c("year", "habitat_method")) %>% 
#   mutate(unknown_method_live_weight_t = ifelse(is.na(unknown_method_live_weight_t), 0, unknown_method_live_weight_t)) %>%
#   mutate(percent_export_lower = 100*dom_live_weight_t/production_t,
#          percent_export_upper = 100*(dom_live_weight_t + unknown_habitat_live_weight_t + unknown_method_live_weight_t)/production_t) %>%
#   ggplot(aes(x = year, color = habitat_method)) +
#   geom_line(aes(y = percent_export_lower)) +
#   geom_line(aes(y = percent_export_upper)) +
#   scale_color_manual(values = habitat_source_colors) +
#   labs(y = "Percent of global production exported", x = "") +
#   facet_wrap(~habitat_method) +
#   theme_bw() +
#   theme(legend.position = "none")

percent_export_by_source <- dom_export_by_source %>%
  left_join(prod_by_source, by = c("year", "habitat_method")) %>% 
  mutate(percent_export = 100*dom_live_weight_t/production_t) %>%
  ggplot(aes(x = year, y = percent_export, color = habitat_method)) +
  geom_line() +
  scale_color_manual(values = habitat_source_colors) +
  labs(y = "% production exported", x = "", color = "Source") +
  theme_bw()

@@

```{r fig1c}
all_degree_summary <-  artis %>% 
  select(year, exporter_iso3c, importer_iso3c) %>%
  distinct() %>%
  group_by(year, exporter_iso3c) %>%
  tally() %>% 
  rename(all_out_degree = n, iso3c = exporter_iso3c) %>%
  full_join(artis %>% 
              select(year, exporter_iso3c, importer_iso3c) %>%
              distinct() %>%
              group_by(year, importer_iso3c) %>%
              tally() %>%
              rename(all_in_degree = n, iso3c = importer_iso3c), 
            by = c("year", "iso3c"))

write.csv(all_degree_summary, "outputs/all_degree_summary.csv", row.names = FALSE)

habitat_method_degree_summary <-  artis %>% 
  select(year, exporter_iso3c, importer_iso3c, habitat_method) %>%
  distinct() %>%
  group_by(year, exporter_iso3c, habitat_method) %>%
  tally() %>% 
  rename(all_out_degree = n, iso3c = exporter_iso3c) %>%
  full_join(artis %>% 
              select(year, exporter_iso3c, importer_iso3c, habitat_method) %>%
              distinct() %>%
              group_by(year, importer_iso3c, habitat_method) %>%
              tally() %>%
              rename(all_in_degree = n, iso3c = importer_iso3c), 
            by = c("year", "iso3c", "habitat_method"))

write.csv(habitat_method_degree_summary, "outputs/habitat_method_degree_summary.csv", row.names = FALSE)

out_degree <- artis %>% 
  filter(habitat_method != "unknown") %>%
  select(year, exporter_iso3c, importer_iso3c, habitat_method) %>%
  distinct() %>%
  group_by(year, exporter_iso3c, habitat_method) %>%
  tally() %>%
  group_by(year, habitat_method) %>%
  ggplot(aes(x = year, y = n, color = habitat_method)) +
  geom_smooth() +
  scale_color_manual(values = habitat_source_colors) +
  labs(y = "Out degree", fill = "Source") + 
  theme_bw()

in_degree <- artis %>% 
  filter(habitat_method != "unknown") %>%
  select(year, exporter_iso3c, importer_iso3c, habitat_method) %>%
  distinct() %>%
  group_by(year, importer_iso3c, habitat_method) %>%
  tally() %>%
  group_by(year, habitat_method) %>%
  ggplot(aes(x = year, y = n, color = habitat_method)) +
  geom_smooth() +
  scale_color_manual(values = habitat_source_colors) +
  labs(y = "In degree", fill = "Source") + 
  theme_bw()

```{r fig1, fig.height = 3, fig.width = 4.5}
ggarrange(global_export_by_source, 
          ggarrange(percent_export_by_source, 
                    out_degree, 
                    ncol = 2, 
                    legend = "none",
                    labels = c("b", "c")), 
          common.legend = TRUE, legend = "bottom",
          ncol = 1, labels = c("a", ""))

@@

```{r SI_top_capture_aqua_imp_exp, fig.height=4, fig.width=4}

# Summarize total imports and exports by habitat and environment
bilateral_habitat_method_summary <- artis %>%
  group_by(year, exporter_iso3c, exporter_region, importer_iso3c, importer_region, habitat_method) %>%
  summarise(live_weight_t = sum(live_weight_t))

write.csv(bilateral_habitat_method_summary, "outputs/bilateral_habitat_method_summary.csv", row.names = FALSE)

# Top exporters, averaged over beginning and end time periods
top_exp_1 <- artis %>% 
  filter(year %in% 1996:2000) %>%
  group_by(exporter_iso3c, method) %>%
  summarise(live_weight_t = sum(live_weight_t)/length(1996:2000)) %>% 
  ungroup() %>%
  group_by(exporter_iso3c) %>%
  mutate(total = sum(live_weight_t)) %>%
  ungroup() %>%
  mutate(exporter_iso3c = fct_reorder(as.factor(exporter_iso3c), total)) %>%
  slice_max(n = 60, order_by = total) %>%
  ggplot(aes(x = live_weight_t/1000000, y = exporter_iso3c, fill = method)) +
  geom_bar(stat="identity", position = "stack") + 
  scale_fill_manual(values = method_colors) +
  lims(x = c(0, 10)) +
  labs(x = "Seafood exports (million t, live weight)", y = "",
       title = "Top 20 seafood \nexporters (1996-2000)", fill = "Production method") +
  theme_minimal()

@@

# Top capture and aquaculture exporters, averaged over beginning and end time periods
top_capture_exp_1 <- artis %>% 
  filter(year %in% 1996:2000, method == "capture") %>%
  group_by(exporter_iso3c, environment) %>%
  summarise(live_weight_t = sum(live_weight_t)/length(1996:2000)) %>% 
  ungroup() %>%
  group_by(exporter_iso3c) %>%
  mutate(total = sum(live_weight_t)) %>%
  ungroup() %>%
  mutate(exporter = countrycode(exporter_iso3c, origin = "iso3c", destination = "country.name")) %>%
  mutate(exporter = fct_reorder(as.factor(exporter), total)) %>%
  slice_max(n = 2*15, order_by = total) %>%
  ggplot(aes(x = live_weight_t/1000000, y = exporter, fill = environment)) +
  geom_bar(stat="identity", position = "stack") + 
  scale_fill_manual(values = environment_colors) +
  lims(x = c(0, 4.75)) +
  labs(x = "Ave. annual exports (million t, live weight)", y = "", fill = "Production environment", 
       title = "Top 15 capture \nexporters (1996-2000)") +
  theme_minimal()

top_capture_exp_2 <- artis %>% 
  filter(year %in% 2015:2019, method == "capture") %>%
  group_by(exporter_iso3c, environment) %>%
  summarise(live_weight_t = sum(live_weight_t)/length(2015:2019)) %>% 
  ungroup() %>%
  group_by(exporter_iso3c) %>%
  mutate(total = sum(live_weight_t)) %>%
  ungroup() %>%
  mutate(exporter = countrycode(exporter_iso3c, origin = "iso3c", destination = "country.name")) %>%
  mutate(exporter = fct_reorder(as.factor(exporter), total)) %>%
  slice_max(n = 2*15, order_by = total) %>%
  ggplot(aes(x = live_weight_t/1000000, y = exporter, fill = environment)) +
  geom_bar(stat="identity", position = "stack") + 
  scale_fill_manual(values = environment_colors) +
  lims(x = c(0, 4.75)) +
  labs(x = "Ave. annual exports (million t, live weight)", y = "", fill = "Production environment",
       title = "Top 15 capture \nexporters (2015-2019)") +
  theme_minimal()

top_aqua_exp_1 <- artis %>% 
  filter(year %in% 1996:2000, method == "aquaculture") %>%
  group_by(exporter_iso3c, environment) %>%
  summarise(live_weight_t = sum(live_weight_t)/length(1996:2000)) %>% 
  ungroup() %>%
  group_by(exporter_iso3c) %>%
  mutate(total = sum(live_weight_t)) %>%
  ungroup() %>%
  mutate(exporter = countrycode(exporter_iso3c, origin = "iso3c", destination = "country.name")) %>%
  mutate(exporter = fct_reorder(as.factor(exporter), total)) %>%
  slice_max(n = 2*15, order_by = total) %>%
  ggplot(aes(x = live_weight_t/1000000, y = exporter, fill = environment)) +
  scale_fill_manual(values = environment_colors) +
  geom_bar(stat="identity", position = "stack") + 
  lims(x = c(0, 4.75)) +
  labs(x = "Ave. annual exports (million t, live weight)", y = "", fill = "Production environment",
       title = "Top 15 aquaculture \nexporters (1996-2000)") +
  theme_minimal()

top_aqua_exp_2 <- artis %>% 
  filter(year %in% 2015:2019, method == "aquaculture") %>%
  group_by(exporter_iso3c, environment) %>%
  summarise(live_weight_t = sum(live_weight_t)/length(2015:2019)) %>% 
  ungroup() %>%
  group_by(exporter_iso3c) %>%
  mutate(total = sum(live_weight_t)) %>%
  ungroup() %>%
  mutate(exporter = countrycode(exporter_iso3c, origin = "iso3c", destination = "country.name")) %>%
  mutate(exporter = fct_reorder(as.factor(exporter), total)) %>%
  slice_max(n = 2*15, order_by = total) %>%
  ggplot(aes(x = live_weight_t/1000000, y = exporter, fill = environment)) +
  scale_fill_manual(values = environment_colors) +
  geom_bar(stat="identity", position = "stack") + 
  lims(x = c(0, 4.75)) +
  labs(x = "Ave. annual exports (million t, live weight)", y = "", fill = "Production environment",
       title = "Top 15 aquaculture \nexporters (2015-2019)") +
  theme_minimal()

ggarrange(top_capture_exp_1, top_capture_exp_2, top_aqua_exp_1, top_aqua_exp_2, common.legend = TRUE, legend = "bottom")

# Top capture and aquaculture importers, averaged over beginning and end time periods
top_capture_imp_1 <- artis %>% 
  filter(year %in% 1996:2000, method == "capture") %>%
  group_by(importer_iso3c, environment) %>%
  summarise(live_weight_t = sum(live_weight_t)/length(1996:2000)) %>% 
  ungroup() %>%
  group_by(importer_iso3c) %>%
  mutate(total = sum(live_weight_t)) %>%
  ungroup() %>%
  mutate(importer = countrycode(importer_iso3c, origin = "iso3c", destination = "country.name")) %>%
  mutate(importer = fct_reorder(as.factor(importer), total)) %>%
  slice_max(n = 2*15, order_by = total) %>%
  ggplot(aes(x = live_weight_t/1000000, y = importer, fill = environment)) +
  geom_bar(stat="identity", position = "stack") + 
  scale_fill_manual(values = environment_colors) +
  lims(x = c(0, 8)) +
  labs(x = "Ave. annual imports (million t, live weight)", y = "", fill = "Production environment", 
       title = "Top 15 capture \nimporters (1996-2000)") +
  theme_minimal()

top_capture_imp_2 <- artis %>% 
  filter(year %in% 2015:2019, method == "capture") %>%
  group_by(importer_iso3c, environment) %>%
  summarise(live_weight_t = sum(live_weight_t)/length(2015:2019)) %>% 
  ungroup() %>%
  group_by(importer_iso3c) %>%
  mutate(total = sum(live_weight_t)) %>%
  ungroup() %>%
  mutate(importer = countrycode(importer_iso3c, origin = "iso3c", destination = "country.name")) %>%
  mutate(importer = fct_reorder(as.factor(importer), total)) %>%
  slice_max(n = 2*15, order_by = total) %>%
  ggplot(aes(x = live_weight_t/1000000, y = importer, fill = environment)) +
  geom_bar(stat="identity", position = "stack") + 
  scale_fill_manual(values = environment_colors) +
  lims(x = c(0, 8)) +
  labs(x = "Ave. annual imports (million t, live weight)", y = "", fill = "Production environment",
       title = "Top 15 capture \nimporters (2015-2019)") +
  theme_minimal()

top_aqua_imp_1 <- artis %>% 
  filter(year %in% 1996:2000, method == "aquaculture") %>%
  group_by(importer_iso3c, environment) %>%
  summarise(live_weight_t = sum(live_weight_t)/length(1996:2000)) %>% 
  ungroup() %>%
  group_by(importer_iso3c) %>%
  mutate(total = sum(live_weight_t)) %>%
  ungroup() %>%
  mutate(importer = countrycode(importer_iso3c, origin = "iso3c", destination = "country.name")) %>%
  mutate(importer = fct_reorder(as.factor(importer), total)) %>%
  slice_max(n = 2*15, order_by = total) %>%
  ggplot(aes(x = live_weight_t/1000000, y = importer, fill = environment)) +
  scale_fill_manual(values = environment_colors) +
  geom_bar(stat="identity", position = "stack") + 
  lims(x = c(0, 8)) +
  labs(x = "Imports (million t, live weight)", y = "", fill = "Production environment",
       title = "Top 15 aquaculture \nimporters (1996-2000)") +
  theme_minimal()

top_aqua_imp_2 <- artis %>% 
  filter(year %in% 2015:2019, method == "aquaculture") %>%
  group_by(importer_iso3c, environment) %>%
  summarise(live_weight_t = sum(live_weight_t)/length(2015:2019)) %>% 
  ungroup() %>%
  group_by(importer_iso3c) %>%
  mutate(total = sum(live_weight_t)) %>%
  ungroup() %>%
  mutate(importer = countrycode(importer_iso3c, origin = "iso3c", destination = "country.name")) %>%
  mutate(importer = fct_reorder(as.factor(importer), total)) %>%
  slice_max(n = 2*15, order_by = total) %>%
  ggplot(aes(x = live_weight_t/1000000, y = importer, fill = environment)) +
  scale_fill_manual(values = environment_colors) +
  geom_bar(stat="identity", position = "stack") + 
  lims(x = c(0, 8)) +
  labs(x = "Imports (million t, live weight)", y = "", fill = "Production environment",
       title = "Top 15 aquaculture \nimporters (2015-2019)") +
  theme_minimal()

ggarrange(top_capture_imp_1, top_capture_imp_2, top_aqua_imp_1, top_aqua_imp_2, common.legend = TRUE, legend = "bottom")
```

```{r SI_top_traders}
total_country_exports <- artis %>% 
  filter(year %in% 2015:2019) %>%
  group_by(exporter_iso3c, method, environment) %>%
  summarise(export_live_weight_t = sum(live_weight_t)/length(2015:2019)) %>%
  mutate(export_live_weight_t = export_live_weight_t/1000000) %>%
  rename("iso3c" = "exporter_iso3c")

total_country_imports <- artis %>% 
  filter(year %in% 2015:2019) %>%
  group_by(importer_iso3c, method, environment) %>%
  summarise(import_live_weight_t = sum(live_weight_t)/length(2015:2019)) %>%
  mutate(import_live_weight_t = import_live_weight_t/1000000) %>%
  rename("iso3c" = "importer_iso3c")

@@

## Regional bilateral flows
```{r region_trend_matrix_by_method, fig.height=5, fig.width=5}
artis_region_method <- artis %>%
  filter(!is.na(importer_region), !is.na(exporter_region), 
         importer_region != "Other nei", exporter_region != "Other nei") %>%
  group_by(year, exporter_region, importer_region, habitat_method) %>%
  summarise(live_weight_t = sum(live_weight_t)) %>%
  ungroup() %>%
  mutate(exporter_importer = paste(exporter_region, " to ", importer_region, sep = ""))

region_trend_matrix_method <- artis_region_method %>% 
  ggplot(aes(x = year, y = live_weight_t/1000000, fill = habitat_method)) +
  geom_area() +
  scale_fill_manual(values = habitat_source_colors) +
  labs(x = "", y = "Trade (million t, live weight)", color = "Ave. annual change in export \n(1000 t live weight)") +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1), 
        legend.position = "none",
        strip.background = element_blank(),
        strip.text.x = element_blank(),
        strip.text.y = element_blank()) +
  facet_grid(rows = vars(exporter_region), cols = vars(importer_region), 
             labeller = label_wrap_gen(width = 5), scales = "free")

# Create basic plot for the legend
artis_region_method %>%
  group_by(year, exporter_region) %>%
  summarise(live_weight_t = sum(live_weight_t)) %>%
  ggplot(aes(x = year, y = live_weight_t, fill = exporter_region)) +
  geom_area() +
  scale_fill_manual(values = region_colors) +
  labs(fill = "Region") +
  theme(legend.position = "bottom")
```

```{r regional_bilateral_trends}
artis_region <- artis_region_method %>%
  group_by(year, exporter_region, importer_region) %>%
  summarise(live_weight_t = sum(live_weight_t)) %>%
  ungroup() %>%
  mutate(exporter_importer = paste(exporter_region, " to ", importer_region, sep = ""))

@@

```{r region_trend_lollipop, fig.height=4, fig.width=8}
region_slopes_ranked <- region_slopes %>%
  mutate(exporter_importer = fct_reorder(exporter_importer, slope)) %>%
  ggplot(aes(x = slope/1000, y = exporter_importer, color = slope, fill = slope)) +
  geom_segment(aes(xend = 0, yend = exporter_importer)) +
  geom_point() +
  scale_color_gradient2(low = "#E24027", mid = "grey70", high = "#1B708F") +
  scale_fill_gradient2(low = "#E24027", mid = "grey70", high = "#1B708F") +
  labs(y = "", x = "Ave. annual change in export (1000 t live weight)") +
  theme_bw() +
  theme(legend.position = "blank")

ggarrange(region_trend_matrix_method, region_slopes_ranked, widths = c(1.5,1))
```

```{r, fig.height=3, fig.width=4}
exports_by_region <- artis_region %>% 
  ggplot(aes(x = year, y = live_weight_t/1000000, fill = importer_region)) +
  geom_area() +
  labs(x = "", y = "", fill = "Importer") +
  scale_fill_manual(values = region_colors) +
  facet_wrap(~exporter_region, ncol = 1) +
  theme_bw() +
    theme(legend.position = "none",
        strip.background = element_blank(),
        strip.text.x = element_blank(),
        axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))

imports_by_region <- artis_region %>% 
  ggplot(aes(x = year, y = live_weight_t/1000000, fill = exporter_region)) +
  geom_area() +
  labs(x = "", y = "", fill = "Exporter") +
  scale_fill_manual(values = region_colors) +
  facet_wrap(~importer_region, nrow = 1) +
  theme_bw() +
  theme(legend.position = "none",
        strip.background = element_blank(),
        strip.text.x = element_blank(),
        axis.text.x = element_blank())

ggarrange(ggarrange(imports_by_region, NULL,
                    ncol = 2, nrow = 1,
                    widths = c(4, 1)),
          ggarrange(region_trend_matrix_method, exports_by_region, 
                    ncol = 2, nrow = 1,
                    widths = c(4, 1)),
          ncol = 1, nrow = 2, 
          heights = c(1, 4))

@@

```{r africa_trade_by_method}
africa_exports <- artis_region_method %>%
  filter(exporter_region == "Africa", 
         importer_region != "Africa") %>%
  group_by(year, habitat_method) %>%
  summarise(live_weight_t = sum(live_weight_t)/1000000) %>%
  ggplot(aes(x = year, y = live_weight_t, color = habitat_method)) +
  geom_line() +
  lims(y = c(0, 3.25)) +
  scale_color_manual(values = habitat_source_colors) +
  theme_minimal() + 
  labs(x = "", y = "Exports (million t, live weight)", color = "Source")

africa_imports <- artis_region_method %>%
  filter(importer_region == "Africa", 
         exporter_region != "Africa") %>%
  group_by(year, habitat_method) %>%
  summarise(live_weight_t = sum(live_weight_t)/1000000) %>%
  ggplot(aes(x = year, y = live_weight_t, color = habitat_method)) +
  geom_line() +
  lims(y = c(0, 3.25)) +
  scale_color_manual(values = habitat_source_colors) +
  theme_minimal() + 
  labs(x = "", y = "Exports (million t, live weight)", color = "Source")

ggarrange(africa_exports, africa_imports, common.legend = TRUE, labels = c("Africa exports", "Africa imports"))
```

# Figure 3: Supply patterns

```{r calculate_supply}
supply <- calculate_supply(artis %>% 
                             # Remove FM trade from supply calculations
                             #filter(hs6 != "230120") %>%
                             rename(habitat = environment), 
                           prod %>% 
                             rename(live_weight_t = production_t)) %>%
  # Add habitat-method column
  mutate(habitat_method = paste(habitat, method, sep =" ")) %>% 
  mutate(habitat_method = case_when(
    str_detect(habitat_method, "unknown") ~ "unknown", 
    TRUE ~ habitat_method
  )) %>% 
  # Set factor levels
  mutate(habitat_method = factor(habitat_method, levels = c("marine capture", "inland capture",
                                                            "marine aquaculture", "inland aquaculture",
                                                            "unknown" ))) %>% 
  left_join(country_metadata %>% 
              select(iso3c, "region" = "owid_region"), by = "iso3c") %>% 
      mutate(supply_no_error = case_when(supply_no_error < 0 ~ 0,
                                     TRUE ~ supply_no_error))

@@

# Fig 3a: Foreign dependence trends
